Exp. 2 Analysis: 2AFC, adults vs. children

### 2020-11-24 analysis/exp2_analysis.Rmd
nicer graphs

require(here)
require(tidyverse)
require(tidyboot)
```

@@

```{r load-model-data}
mdat <- read_csv("agent-data/curiodrop-model-8-23-20.csv")
mdat <- read_csv("agent-data/curiodrop_0.csv") # most trials close to chance
mdat <- read_csv("agent-data/curiodrop_1.csv")
mdat <- read_csv("agent-data/curiodrop_2.csv")

@@

```{r load-human-data, include=F, echo=FALSE}
raw = read_csv("exp2-mturk-data/MturkAdultDrop-Data-Combined.csv")
# row 1 is empty, row 2 should be header
d = raw[3:nrow(raw),]
names(d) = raw[1,]
d[,"NA"] = NULL
names(d) <- make.unique(names(d))
d[which(is.na(d$Exclude)),]$Exclude = 'N'

@@

```{r adult-model-correlation}
# model vs. adult (trial level)
cor.test(adult_trial_agg$chose_target, model_trial_agg$chose_target)
```

@@

```{r load-child-data}
rawch <- read_csv("human-data/DevoDrop_data_raw - Combined.csv") # children data
rawch[which(is.na(rawch$Exclude)),]$Exclude = 'N'

@@

@@

```{r per-trial-comparison}
adult_long <- adult_long %>% rename(ID = ResponseId) %>%
  mutate(Age = "adult") %>%
  select(ID, Age, Trial, choice, drop, target, relation, chose_target)

@@

combo_dat %>% group_by(drop, target, relation, AgeGroup) %>%
  summarise(chose_target = mean(chose_target, na.rm=T)) %>%
  pivot_wider(names_from = AgeGroup, values_from = chose_target) %>%
  ggplot(aes(x=adult, y=child, group=relation, color=relation)) + 
    geom_point(alpha=.7) + theme_bw() + ylim(0,1) + xlim(0,1) + 
  geom_abline(xintercept=0, slope=1, linetype="dashed") #+
  #geom_text(aes(label=target)) #

@@

combo_dat %>% 
  mutate(AgeGroup = ifelse(Age=="adult", "adult", 
                           ifelse(Age=="3" | Age=="4", "3-4 yo", "5-7 yo"))) %>%
  group_by(ID, AgeGroup, relation) %>% # alt, 
  summarize(chose_target=mean(chose_target, na.rm=T)) %>%
  group_by(relation, AgeGroup) %>%
  tidyboot_mean(chose_target) %>%
  ggplot(aes(x=relation, y=mean, fill=AgeGroup)) + geom_bar(stat="identity", position=pos) + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = pos) + 
  geom_hline(aes(yintercept=.5), linetype="dashed") + theme_classic() + ylim(0,1)
```

@@

```{r}
# library(psych) # has a (Cronbach's) alpha function that takes a covariance matrix

@@

# overall
sh_subj = split_half_subj_cor(combo_dat)
mean(sh_subj) # .736

sh_subj_adult = split_half_subj_cor(subset(combo_dat, AgeGroup=="adult"))
mean(sh_subj_adult) # .791

sh_subj_child = split_half_subj_cor(subset(combo_dat, AgeGroup=="child"))
mean(sh_subj_child) # .56

sh_subj_contain = split_half_subj_cor(subset(combo_dat, relation=="contain"))
mean(sh_subj_contain) # .649

sh_subj_support = split_half_subj_cor(subset(combo_dat, relation=="support"))
mean(sh_subj_support) # .619

# split items in half, check cor between halves...GK: I don't think we care about this
split_half_item_cor <- function(dat, nsim=100) {
  trials = unique(dat$Trial)
  cors = rep(NA, nsim)
  for(i in 1:nsim) {
    idx1 = sample(trials, size=length(trials)/2)
    idx2 = setdiff(trials, idx1) # nonsampled items
    # h1 <- dat %>% filter(is.element(idx1, Trials)) %>% group_by(ID, AgeGroup)

    cors[i] = cor()
  }
  return(cors)
}

>>>>

require(here)
require(tidyverse)
require(tidyboot)
require(gridExtra)
```

@@

```{r load-model-data, include=F}
mdat <- read_csv("agent-data/curiodrop-model-8-23-20.csv")
mdat <- read_csv("agent-data/curiodrop_0.csv") # most trials close to chance
mdat <- read_csv("agent-data/curiodrop_1.csv")
mdat <- read_csv("agent-data/curiodrop_2.csv")

@@

```{r load-human-data, echo=FALSE}
raw = read_csv("exp2-mturk-data/MturkAdultDrop-Data-Combined.csv")
# row 1 is empty, row 2 should be header
d = raw[3:nrow(raw),]
names(d) = raw[1,]
d[,"NA"] = NULL
names(d) <- make.unique(names(d))
d[which(is.na(d$Exclude)),]$Exclude = 'N'

@@

```{r adult-model-correlation, include=F}
# model vs. adult (trial level)
cor.test(adult_trial_agg$chose_target, model_trial_agg$chose_target)
```

@@

```{r load-child-data, echo=F}
rawch <- read_csv("human-data/DevoDrop_data_raw - Combined.csv") # children data
rawch[which(is.na(rawch$Exclude)),]$Exclude = 'N'

@@

## Can we estimate a single item "interestingness" from the 2AFC data?

```{r}
table(ch_long$drop, ch_long$choice)
```

@@

```{r per-trial-comparison, fig.width=5, fig.height=5}
# add vert and horiz error bars 
adult_long <- adult_long %>% rename(ID = ResponseId) %>%
  mutate(Age = "adult") %>%
  select(ID, Age, Trial, choice, drop, target, relation, chose_target)

@@

# 12 NAs somewhere

combo_dat %>% group_by(drop, target, relation, ID) %>%
  group_by(drop, target, relation, AgeGroup) %>%
  tidyboot_mean(chose_target, na.rm=T) %>%
  select(-n, -empirical_stat) %>%
  pivot_wider(names_from = AgeGroup, values_from = c(mean, ci_lower, ci_upper)) %>%
  ggplot(aes(x=mean_adult, y=mean_child, group=relation, color=relation)) + 
    geom_point(alpha=.6) + 
    geom_errorbar(aes(ymin=ci_lower_child, ymax=ci_upper_child), alpha=.6) +
    geom_errorbarh(aes(xmin=ci_lower_adult, xmax=ci_upper_adult), alpha=.6) + 
    theme_bw() + ylim(0,1) + xlim(0,1) + 
    xlab("Adults' Choice Proportions") + ylab("Children's Choice Proportions") + 
    geom_abline(xintercept=0, slope=1, linetype="dashed") +
    geom_smooth(method = "lm") 
  #geom_text(aes(label=target)) #

@@

p1 <- combo_dat %>%
  mutate(AgeGroup = ifelse(Age=="adult", "adult", "child"),
         AgeGroup = factor(AgeGroup, levels=c("child", "adult"))) %>%
  group_by(ID, AgeGroup, relation) %>% # alt, 
  summarize(chose_target=mean(chose_target, na.rm=T)) %>%
  group_by(relation, AgeGroup) %>%
  tidyboot_mean(chose_target) %>%
  ggplot(aes(x=relation, y=mean, fill=AgeGroup)) + geom_bar(stat="identity", position=pos) + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = pos) + 
  geom_hline(aes(yintercept=.5), linetype="dashed") + theme_classic() + ylim(0,1)

p2 <- combo_dat %>% 
  mutate(AgeGroup = ifelse(Age=="adult", "adult", 
                           ifelse(Age=="3" | Age=="4", "3-4 yo", "5-7 yo"))) %>%
  group_by(ID, AgeGroup, relation) %>% # alt, 
  summarize(chose_target=mean(chose_target, na.rm=T)) %>%
  group_by(relation, AgeGroup) %>%
  tidyboot_mean(chose_target) %>%
  ggplot(aes(x=relation, y=mean, fill=AgeGroup)) + geom_bar(stat="identity", position=pos) + 
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), position = pos) + 
  geom_hline(aes(yintercept=.5), linetype="dashed") + theme_classic() + ylim(0,1)

grid.arrange(p1, p2, nrow = 1)
```

@@

```{r, echo=T}
# library(psych) # has a (Cronbach's) alpha function that takes a covariance matrix

@@

# overall
sh_subj = split_half_subj_cor(combo_dat)

sh_subj_adult = split_half_subj_cor(subset(combo_dat, AgeGroup=="adult"))

sh_subj_child = split_half_subj_cor(subset(combo_dat, AgeGroup=="child"))

sh_subj_contain = split_half_subj_cor(subset(combo_dat, relation=="contain"))

sh_subj_support = split_half_subj_cor(subset(combo_dat, relation=="support"))

# split items in half, check cor between halves...GK: I don't think we care about this

```
Split-half reliability for all subjects: `r round(mean(sh_subj),2)`.
Split-half reliability for adults: `r round(mean(sh_subj_adult), 2)`.
Split-half reliability for children: `r round(mean(sh_subj_child), 2)`.

Split-half reliability for contain relations: `r round(mean(sh_subj_contain), 2)`.
Split-half reliability for support relations: `r round(mean(sh_subj_support), 2)`.
